Motion Illusion Detection and Creation

### 2019-12-20 1-illusion/report/report.tex
add details to illusion detection, illusion generation and related work

@@

@@

@@

@@

@@

\section{Conclusion}
\label{sec:conclusion}
The conclusion of the paper \dots

>>>>

  Based on the motion reproduction model, we are able to represent the illusory motion with optical flows. To be more exact, the model generates one vector at each pixel, which indicates the strength and direction there. However, there is still some work to be done on the flow so as to quantify the intensity of rotating.

  The first reason is that we prefer an objective criteria to determine the existence of motion illusion. Admittedly, optical flows can be a straightforward way to illustrate. For example, most people would concur that the first optical flow in Fig.~\ref{fig:standard_rotating_flows} is rotating, but different people may have different idea about the how strong the feeling is. Also, the question that whether flows are rotating can be more difficult to answer when the flows are more complex, such as the second flows in Fig.~\ref{fig:standard_rotating_flows}.

  Another reason for establishing quantitative standards is that numerical measurement is necessary if we want to use Generative Adversarial Network(GAN) or other similar optimization method to produce intensive illusion. Generally, GAN is composed of two neural networks, one for generation and the other for discrimination. To apply the method, the discriminative network needs to know how "good" the generated photo is. In other word, it should evaluate the rotating intensity objectively.

  \begin{figure}[t]
    \centering
    \includegraphics[width=0.4\linewidth,height=0.4\linewidth]{fig/standard_rotating.pdf}
      \includegraphics[width=0.4\linewidth, height=0.4\linewidth]{fig/non_standard_rotating.pdf}
    \caption{Examples of rotating flows.}
    \label{fig:standard_rotating_flows}
  \end{figure}

  Given adequate reasons to build an objective standard, what is left to do is to use mathematical tools to devise such a standard. There are several ways to achieve the goal.

  Summing up all the norms can be the most simple solution. The greater the sum is, the more the flows are moving. In spite of this, norms only use partial information of the flow, regardless of the direction, which can be equally important in detecting rotation. Similar to the case that histogram contains no information about the distribution of contents, we have no idea whether one or more "sources" exist in the flows indeed.

  If we want to make use of direction as well as norm, a natural idea is to borrow the notion of "torque" in physics. Torque is the product of the magnitude of the force(flow) and the perpendicular distance of the line of action of force(flow) from the axis of rotation. It can describes how strong the inclination to rotate clockwise is on a two-dimensional plane. The main obstacle to fulfilling the algorithm is that some prior knowledge about source is necessary. On the one hand, the accuracy to choose the right source can play a big role in the final result. On the other hand, if we have multiple sources in a flow graph, then we also need to allocate each flow to its corresponding source, which can be another difficulty.

  There are also other ways to judge the intensity of rotation from flows. For instance, Riemannian geometry provides us with some tools to assess some qualities of flows, but we don't consider it as our way to implement mainly because of its computational complexity. Besides, it is more suitable in continuous cases, while the flows calculated from the reproduction model is discrete.

@@

  In our experiment, we propose to use flownet to replace the traditional optical flow detection procedure. Flownet is comprised of appropriate convolutional neural networks (CNNs), which are capable of solving the optical flow estimation problem as a supervised learning task.

  Traditionally, an optical flow detector is composed of several components. Sensors are carried on platform, which is responsible for removing undesirable motion, or background noise. \cite{sebok1997optical} After that, we apply well-designed filters, such as gradient for flow detection. \cite{naoya1990optical} Some other parts may be responsible for flow prediction, based on the input from the preceding components. Such a procedure is largely designed to detect and predict motions between different frames. To the best of our knowledge,  no previous work has been done on the prediction of flow given one frame. Moreover, it is too difficult to accomplish the task with traditional methods, given that the majority of them use the difference between frames as their main features.

  Things can be different when it comes to convolutional neural network. It integrates these parts into a black box and directly output the prediction of flows, while what we need to do is to send input and receive output. With flownet, it is convenient to back propagate the error back to the prednet and further propagate it to the generator under the framework of GAN. Therefore, the generator assists in improving the quality of illusory image.

  Although it is relatively easier to use flownet, we can not escape the shortcomings in applying CNN. First of all, it takes more time and CPU resources to compute the result for each pair of input, although it truly alleviate the pressure to design good algorithms for estimation and prediction by ourselves. Besides, the black box nature impose trouble in modifying the model, while we do benefit from the simple usage of such a network.

  In order to incorporate flownet into our illusion detecting procedure, we need to reconstruct the output of flownet, which is shown in vector field, into something more quantifiable to fit the context of our model, just as described in part B. Apart from that, we just send two identical pictures into the model, and get output. The flownet should be adjusted and we need to finely tune the model for better performance if it is further used to form the discriminator.

@@

  GAN was first proposed as estimating generative models in 2014. Similar to a a minimax two-player game, the generative model G is trained to maximize the probability of discriminative model D making a mistake, while D tries to better its performance in discrimination. \cite{goodfellow2014generative} In 2015, deep convolutional generative adversarial networks (DCGANs) to tackle unsupervised learning. It learns good image representations by training GANs, and later reuses parts of the generator and discriminator networks as feature extractors for supervised tasks.\cite{radford2015unsupervised} The generator and the discriminator are trained alternatively to improve their quality, where the proper design of training loss has huge influence on the final model.

  When it comes to our scenario, a working discriminator has been chosen, thus we only need to design and train the generator. Here, the discriminator has already been trained and the training of discriminator is offline, therefore, the whole model is asymmetric.

@@

  In theory, it is possible to construct a traditional DNN generator. However, consider the fact that we do not have too much pictures that can generate rotating illusion and we do not know much about principle behind the illusion, it can be difficult to write a model from scratch.
  As a solution to the above problem, we may have to write a simpler generator, with more information given. For example, we may assume that we have a down-sampled picture as input, and what we need to do is to provide more details so that the output may seem to be rotating. Besides, there are also other properties that we can use. For example, we can make the assumption that the photo is symmetric, which can also make the generating procedure much easier.

@@

  The illusion intensity itself is not enough. When a human looks at a picture, he will extract certain information from it, rather than look at all the pixels one by one. Some details may be omitted while others may be closely examined. In contrast, most computing-based models don't have the function, therefore are not immune to slight changes in input sometimes. In some cases, the original photos may not be rotating, but if we add rotating noise which is almost invisible to human eyes, the detection model can output wrong results. Thus, other sanity constraint criteria is also a necessity. We may apply local entropy calculation as a method, where whether or not it is a good criteria is another question.

@@

  Probably the most closely related work is done by Eiji Watanabe et al. They propose to use natural scene videos of the self-motion of the viewer to train deep neural networks based model, PredNet, so as to detect rotational illusory motion. \cite{watanable2018illusory} Despite our work is based on similar networks, we do our experiment on a wider range of rotating illusions rather than one or two single pictures. What's more, we also propose an architecture to use GAN to generate pictures with similar illusory effects.

  A more recent work by Emily use a pre-trained neural network to see if the network exhibits similar perceptual biases as human. The researcher examines four classic illusions,  Muller-Lyer, Ebbinghaus,  Ponzo and Vertical-Horizontal, and finds out that deep neural networks trained exclusively for object recognition exhibit the Muller-Lyer illusion, but not other illusions. \cite{ward2019exploring} . Gomez-Villa et al. also reveal that CNNs can be deceived by color illusion. \cite{gomez2018convolutional}

  To the best of our knowledge, there are not many other researchers trying to apply neutral networks to the detection of illusion. In spite of this, CNNs have already been used for similar work such as object recognition. Liang et al. are inspired by the difference between feed-forward  architecture of CNN and abundant recurrent connections in the visual system, and propose a recurrent CNN (RCNN) for object recognition by incorporating recurrent connections into each convolutional layer.\cite{liang2015recurrent}

  \section{Conclusion}
  \label{sec:conclusion}

  The conclusion of the paper \dots
